### 2021-04-08 papers/SYRCoSE/regmachine-eventstruct.tex
Regmachine: union of two relations

Next, following the theory of axiomatic weak memory models~\cite{Lahav-al:PLDI17},
we define the causality relation of the register machine's event structure
as a transitive closure of two relations~---~\emph{program order} 
and \emph{reads-from}, denoted as $\lPO$ and $\lRF$ correspondingly.

>>>>

Next, following the theory of axiomatic weak memory models~\cite{Lahav-al:PLDI17},
we define the causality relation of the register machine's event structure
as the reflexive transitive closure of the union of two relations~---~\emph{program order} 
and \emph{reads-from}, denoted as $\lPO$ and $\lRF$ correspondingly.
